Forecasting 2024 US election using linear regression

### 2024-10-25 paper/paper.qmd
update the appendix B and C, with methodology and copy of survey

### Methodology

#### Sampling Approach

@@

##### Step 1: Define the Sampling Data

@@

##### Step 2: Calculate Actual Voters

@@

##### Step 3: Calculate Composite Measure of Size

@@

##### Step 4: Allocate Sample Based on Turnout

@@

@@

| **Region**    | **States**                                                                                                                                                 |
|------------------------------------|------------------------------------|
| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |

@@

| **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
|-----------|-----------|-----------|-----------|-----------------|-----------|
| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 64              |
| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 60              |
| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 107             |
| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 68              |

: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout{#tbl-sample_size}

@tbl-sample_size shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP). The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.

Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income. This ensures that each demographic group is represented proportionally to the U.S. population.

Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.

@@

I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.

Online Recruitment: Use targeted advertisements on social media platforms (e.g., Facebook, Instagram) and popular news websites. A portion of the budget will be allocated to recruiting via established online panel providers such as Qualtrics or YouGov. Phone and SMS Polling: To capture voters who may not engage online, I will employ live phone interviews using Random Digit Dialing (RDD) and SMS text polls, ensuring coverage of both landline and mobile users. In-Person Recruitment: In key battleground states, local fieldworkers will be deployed to recruit voters who may not be reached through digital or phone methods, ensuring a geographically diverse sample. 3. Data Validation and Quality Control Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
Voter Verification: Respondents will be asked to confirm their voter registration status, and a subset of the sample will be cross-checked with voter databases to validate their responses. Attention Checks: To minimize random or disengaged responses, I will include attention checks (e.g., questions asking respondents to select a specific answer) throughout the survey. Duplicate Prevention: Respondent IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual. Weighting: Post-stratification weighting will be applied to adjust for any demographic imbalances in the final sample. Weighting factors will be based on age, gender, race, education, and voting history to match U.S. population benchmarks.

4.  Poll Aggregation and Forecasting Model In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.

Poll Aggregation: I will collect data from publicly available polls (e.g., FiveThirtyEight, RealClearPolitics) and develop a weighted average based on the reliability of each poll, sample size, and recency. Weighting by Pollster Quality: Pollsters will be rated based on their historical accuracy, sample sizes, and transparency in methodology. More reliable polls will be weighted higher in the aggregation model. Predictive Modeling: I will use a Bayesian predictive model that incorporates current polling data, historical voting patterns, economic indicators, and other key variables to generate a probabilistic forecast of the election outcome.

5.  Questionnaire Design The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions. It will be short and simple, taking no more than 10 minutes to complete. Survey Link The survey has been implemented using Google Forms. Here is the link to access the survey:\
    https://forms.gle/BAZhkWDyLxAibwvu5

Budget Breakdown Here is a proposed allocation of the \$100,000 budget:\
Survey Platform and Software Costs: \$5,000 for survey hosting on Google Forms and Qualtrics. Recruitment Costs: \$40,000 for online panel recruitment, social media ads, and targeted outreach. Phone and SMS Polling: \$20,000 to cover live phone interviews and SMS polling. Fieldwork in Key States: \$15,000 for in-person recruitment in battleground states. Data Validation and Cleaning: \$10,000 for voter verification, attention checks, and cleaning services. Poll Aggregation and Modeling Tools: \$7,000 for the development of a poll aggregation tool and Bayesian forecasting model. Miscellaneous Costs: \$3,000 for administrative costs, project management, and reporting.

>>>>

### Sampling Approach

@@

#### Step 1: Define the Sampling Data

@@

#### Step 2: Calculate Actual Voters

@@

#### Step 3: Calculate Composite Measure of Size

@@

#### Step 4: Allocate Sample Based on Turnout

@@

Based on the recruitment method we discussed later, our sampling frame could be all registered voters in online panels like Qualtrics and YouGov and the millions of U.S. voters who are reachable via social media platforms like Facebook and Instagram.

@@

| **Region**    | **States**                                                                                                                                                 |
|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------|
| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |

@@

| **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
|-------------|-----------------------|------------------------|------------|-------------------------------------------|-----------------|
| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 143             |
| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 91              |

: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout {#tbl-samplesize}

@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP). The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.

**Stratification Variables**: After determining the number of respondents to be sampled from each region, stratified sampling will be applied across key demographic categories such as age, gender, race/ethnicity, and education level. This approach helps ensure that the final sample accurately reflects the diversity of the U.S. voting population by proportionally representing each subgroup within each region. To address potential non-response bias, post-stratification weighting[^1] will be applied, adjusting for any imbalances caused by differences in response rates across demographic groups. The sample will be stratified across several key demographic and geographic variables to ensure proportional representation of the U.S. voting population. These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%). Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%). Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%). For each variable, U.S. Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population. Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.

[^1]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.

@@

Due to budget constraints, we will focus on online recruitment methods, which offer a cost-effective and efficient way to reach a diverse and representative sample of voters across the country.

Online Recruitment: With the objective of surveying 400 respondents, we will focus our resources on implementing the survey and ensuring high-quality data collection. The survey will be developed in-house, and respondents will be recruited using online survey platforms. The recruitment approach is as follows:

Sample Size Distribution Across Platforms

Online Panel Providers (Qualtrics, YouGov): 200 respondents will be recruited through reputable online panel providers like Qualtrics and YouGov, known for high-quality samples with verified voter registration status. This recruitment source provides a strong base of quality data, given the stringent participant verification process in place.

Social Media Recruitment: We plan to recruit 400 respondents through targeted social media panels on platforms such as Facebook and Instagram. Given the typically lower data quality from social media recruitment, we anticipate that 50% of responses may be invalid. To compensate, we will oversample from this group, aiming to gather a sufficient number of valid and high-quality responses. To attract participants, each respondent will receive a small monetary reward (such as a gift card) for completing the survey. Targeted ads and eligibility screening will be used to reach respondents who meet key criteria, such as age and U.S. voter registration status. This approach helps ensure that those recruited are likely to be eligible voters.

#### Respondent Validation

To ensure high data quality and accuracy, respondent validation will be conducted through multiple checks and verification processes. This process ensures that only eligible and relevant participants are included in the survey, maintaining the integrity of the sample.

Voter Registration Verification:

Respondents will be required to confirm their voter registration status, with a portion of the sample cross-referenced against voter registration databases or verified through reputable online panel providers like Qualtrics or YouGov. This step ensures that the survey includes only registered and likely voters, crucial for representing the target population accurately. Screening and Eligibility Questions:

Respondents will complete a set of screening questions to verify eligibility criteria, such as age (18 or older) and U.S. citizenship. Only those meeting these criteria will be allowed to proceed with the survey. Attention Checks:

To detect and filter out inattentive or disengaged participants, attention-check questions will be embedded throughout the survey (e.g., asking respondents to select a specific answer to verify attentiveness). Respondents who fail these checks may be excluded from the final sample. Duplicate Prevention:

Unique identifiers such as IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual, ensuring that each response represents a unique participant. Post-Survey Data Cleaning:

After data collection, responses will be reviewed for consistency and completeness. Inconsistent responses or incomplete surveys will be removed, maintaining the quality and reliability of the dataset. By implementing these respondent validation steps, the survey methodology ensures that data collected reflects only eligible, registered, and attentive respondents, thereby enhancing the validity and accuracy of the survey results.

### Poll Aggregation

After getting the survey response, we will aggregate polls from two recruitment sources: online panel providers and social media platforms.To weight the two panels effectively, we will first identify key demographic variables for stratification, such as age, gender, race/ethnicity, and education level, and establish population proportions using U.S. Census data or other reliable sources. For the online panel (200 respondents), we will compare the demographic distribution of respondents to these population benchmarks, calculating weights based on the degree of under- or over-representation. Similarly, we will perform this analysis for the social media panel (400 respondents) to determine its weights. Once we have calculated weights for each panel, we will combine them into a single weighting scheme that reflects the overall demographic composition of the target population. During data analysis, we will apply these weights to the responses, ensuring that underrepresented groups have a greater influence on the results while adjusting for those that are overrepresented. Finally, we will conduct post-stratification adjustments to confirm that the combined sample accurately mirrors the true characteristics of the U.S. voting population, providing reliable insights into voter preferences and behaviors.

### Survey Design

The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions. It will be short and simple, taking no more than 15 minutes to complete. Survey Link The survey has been implemented using Google Forms. Here is the link to access the survey:\
https://forms.gle/BAZhkWDyLxAibwvu5

### Budget Breakdown

Budget Breakdown With a total budget of \$100,000, the allocation for various components of the survey implementation and data collection is as follows:

Survey Design and Development: \$2,000 This portion covers the design and development of the survey, including question formatting, testing, and integration with online platforms like Qualtrics and social media platforms. Ensuring the survey is user-friendly and addresses key research questions is essential for high-quality data collection. Online Panel Providers (Qualtrics, YouGov): \$80,000 (200 respondents at \$400 per respondent) We will recruit 100 respondents via reputable online panel providers like Qualtrics and YouGov. These platforms ensure high-quality responses through verified voter registration, but they come at a higher cost per respondent due to their validation processes.

Social Media Recruitment (Facebook, Instagram): \$12,000 (400 respondents at \$30 per respondent) 400 respondents will be recruited using targeted social media ads. Since we expect 50% of responses to be invalid, oversampling will allow us to achieve a final valid sample of 200 respondents. The cost per respondent is lower than online panel providers, but rigorous validation and filtering are required to ensure data quality.

Data Validation and Quality Control: \$6,000 This covers voter registration verification, attention checks within the survey, and extensive post-collection filtering, particularly for social media responses. Ensuring the integrity and accuracy of the data is crucial to minimize biases and errors.

## U.S. Presidential Election Polls Survey

---
title: "U.S. Presidential Election Polls Survey"
author: "Diana Shen, Jinyan Wei, Jerry Yu"
date: "`r Sys.Date()`"
output: pdf_document
---

Welcome

Welcome to our 2024 U.S. Presidential Election Polls Survey. Your participation in this survey is vital in helping us understand voters' preferences and opinions on key issues. Rest assured that your responses are anonymous and will only be used for statistical analysis.

This survey is for academic research in Statistics. It consists of 26 carefully designed questions and should take approximately 12-15 minutes to complete.

For any questions or concerns regarding this survey, please contact:\
**Email:** diana.shen\@mail.utoronto.ca

------------------------------------------------------------------------

Privacy Notice for Respondents

Your privacy is our priority. In this survey, your responses are completely anonymous, ensuring that no one can link your answers back to you. We encourage you to share your true opinions, as this survey is conducted by a neutral, nonpartisan entity. Your data will only be used for research purposes, and you will not be identified individually. If you have concerns, we ask for your feedback at the end of the survey to ensure transparency and trust.

------------------------------------------------------------------------

Section 1: Survey Questions

1.  **Do you approve or disapprove of the job Joe Biden is doing as President?**

    -   Approve
    -   Disapprove
    -   Neutral or no opinion

2.  **What is your party registration or affiliation?**

    -   Democrat
    -   Republican
    -   Independent/ Other
    -   Prefer not to say
    -   Other: __________

3.  **If the Presidential Election were held today, would you vote for Kamala Harris or Donald Trump?**

    -   Kamala Harris
    -   Donald Trump
    -   Someone else
    -   Undecided
    -   Prefer not to say

4.  **Although you are undecided, which candidate do you lean toward?**(Jump to this question only if responders choose undecided in Question 3)

    -   Kamala Harris
    -   Kamala Harris
    -   Donald Trump

5.  **How favorable are you towards the following candidates?**

    |               | Very unfavorable | Unfavorable | Moderate | Favorable | Very favorable |
    |---------------|------------------|-------------|----------|-----------|----------------|
    | Kamala Harris |                  |             |          |           |                |
    | Donald Trump  |                  |             |          |           |                |

6.  **How certain are you about your candidate choice?**

    -   Very certain
    -   Somewhat certain
    -   Not certain

7.  **How do you plan to cast your vote?**

    -   In-person on election day
    -   Early voting in-person
    -   By mail
    -   Unsure

8.  **Did you vote in the 2020 U.S. presidential election?**

    -   Yes
    -   No
    -   Prefer not to say

9.  **If you voted in 2020, who did you vote for?**

    -   Joe Biden
    -   Donald Trump
    -   Other
    -   Prefer not to say

10. **Imagine the following candidates: Candidate A favors cutting taxes but has a weak stance on climate change, and Candidate B focuses on healthcare but supports increased military spending. Who would you vote for?**

    -   Candidate A
    -   Candidate B

11. **Imagine two candidates: Candidate A supports education reform but plans to cut social security, and Candidate B focuses on green energy but raises taxes. Who would you vote for?**

    -   Candidate A
    -   Candidate B

12. **What do you think is the most important issue facing the United States?**

    -   Economy
    -   Healthcare
    -   Climate Change
    -   Immigration
    -   National Security
    -   Education
    -   Social Security
    -   Other: __________

13. **Select option 3 from the list below:**

    -   Option 1
    -   Option 2
    -   Option 3
    -   Option 4

14. **How important is the economy in deciding your vote?**

    -   Not important
    -   1
    -   2
    -   3
    -   4
    -   5
    -   Very important

15. **How important is climate change in deciding your vote?**

    -   Not important
    -   1
    -   2
    -   3
    -   4
    -   5
    -   Very important

16. **How important is healthcare in deciding your vote?**

    -   Not important
    -   1
    -   2
    -   3
    -   4
    -   5
    -   Very important

17. **How closely are you following news about the 2024 U.S. presidential election?**

    -   Very closely
    -   Somewhat closely
    -   Not closely

18. **Which social media platforms do you use to get political news?** (Select all that apply)

    -   Facebook
    -   Twitter
    -   Instagram
    -   YouTube
    -   None

------------------------------------------------------------------------

Section 2: Demographic Information

**Privacy Notice for Demographic Information Collection**\
Your demographic information is collected anonymously and will be used for statistical purposes only, helping us analyze trends across different groups. We ensure that your individual responses cannot be traced back to you, maintaining full confidentiality. Your privacy and honest participation are important to us.

1.  **What is your age group?**
    -   18-24
    -   25-34
    -   35-44
    -   45-54
    -   55-64
    -   65+
2.  **Region:**
    -   Northeast
    -   South
    -   Midwest
    -   West
3.  **For statistical purposes only, can you please tell me your ethnicity?**
    -   Hispanic or Latino of any race
    -   White or Caucasian
    -   Black or African American
    -   Asian
    -   Other or multiple races
4.  **Can you please tell me your gender?**
    -   Men
    -   Women
    -   Other
    -   Prefer not to say
5.  **What is the highest level of education you have attained?**
    -   High school or less
    -   Some college
    -   Bachelor’s degree
    -   Graduate degree
6.  **What is your household annual income level?**
    -   Less than \$50,000
    -   \$50,000 - \$100,000
    -   Over \$100,000
    -   Prefer not to say

------------------------------------------------------------------------

Section 3: Feedback

1.  **Do you have any concerns or feedback regarding the survey?**\
    Your feedback is important to us and will help ensure transparency and trust in the research process.

------------------------------------------------------------------------

Thank You

Thank you for taking the time to complete this survey. Your honest feedback is invaluable and will contribute greatly to our research. We appreciate your participation!
